\bf Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-06-01 nips2015.tex
ENH: more

\subsection{Some notation and terminology}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$.
%% For example, $((-2, \pi))_+ = (max(-2, 0),
%% max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
denotes the $m$-by-$n$ matrix of zeros.

@@

Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by $i_C(x) = 0$
if $ x \in C$; $i_c(x) = \infty$ otherwise.

Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  \textit{proper} (meaning that it is not identically $\infty$) convex
  function.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
The \textit{convex conjugate} of $f$ is the function $f^*:
\mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
  \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
Given $\tau > 0$, the \textit{proximal operator}
of $f$ at rank $\tau$, denoted $\prox_{\tau f}$, is the
function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
unique) solution of the problem $\underset{z \in
  \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)$.

@@

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

@@

\begin{definition}(\textbf{Nash $(\rho,\epsilon)$-equilibria})
Given $\rho > 0$ and $\epsilon > 0$, a Nash $(\rho,\epsilon$)-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that ...

\subsection{Outline of the article}
We develop a $\mathcal{O}(1/\epsilon)$ primal-dual algorithm for computing Nash
$\epsilon$-equilibria for sequential two-person zero-sum games with
imcomplete information and perfect recall.

@@

\cite{gilpinfirst} proposed a modified verson of the technqiues in \cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| / \delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in terms of the number of calls made to a first-order oracle (for example, Nesterov's optimal gradient \cite{nesterov1983}). Here $\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain \textit{condition number} for the game.
It should be noted however that
\begin{itemize}
\item[--] though \cite{gilpinfirst} proved that we always have $\delta > 0$, this constant can be arbitrarily small; and most importantly,
\item[--] the reported linear convergence rate is not in terms of basic operations (addition, multiplication, matvec, clipping, etc.), but in terms of the number of calls to a first-order oracle. Of course, the existence of a linear algorithm for solving \eqref{eq:gilpin} is improbable, as the usual strong-convexity conditions are absent.
\end{itemize}

%% It should be noted that the EGT and its precursors have had considerable success in the signal processing communities, as can be seen in \cite{NestaCandès, eduard, etc.} and the references therein.

>>>>

\subsection{Notation and terminology}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
%% by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$.
%% For example, $((-2, \pi))_+ = (max(-2, 0),
%% max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.
$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real
matrices, $I_m$ denotes the $m$-by-$m$ identity matrix, and $0_{m,n}$
denotes the $m$-by-$n$ matrix of zeros.

@@

Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by $i_C(x) = 0$
if $ x \in C$; $i_c(x) = \infty$ otherwise.
Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
$\dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}$. If $\dom(f) \ne
\emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
Given $\tau > 0$, the \textit{proximal operator}
of $f$ at rank $\tau$, denoted $\prox_{\tau f}$, is the
function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
unique) minimizer of the $1$-strongly convex function $\mathbb{R}^n
\rightarrow (-\infty,+\infty]$, $z\mapsto \frac{1}{2}\|z - x\|^2 +
  \tau f(z)$.

@@

\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

@@

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash $(\rho,\epsilon$)-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that ...
\end{definition}

\subsection{Outline of the article}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm for computing Nash $(\rho, \epsilon$)-equilibria for
sequential two-person zero-sum games with imcomplete information and
perfect recall.

@@

\cite{gilpinfirst} proposed a modified verson of the technqiues in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle (for
example, Nesterov's optimal gradient \cite{nesterov1983}). Here
$\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain
\textit{condition number} for the game. It should be noted however that
\begin{itemize}
\item[--] though \cite{gilpinfirst} proved that we always have $\delta
  > 0$, this constant can be arbitrarily small; and most importantly,
\item[--] the reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. Of
  course, the existence of a linear algorithm for solving
  \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  conditions are absent.

\end{itemize}

%% It should be noted that the EGT and its precursors have had
%% considerable success in the signal processing communities, as can
%% be seen in \cite{NestaCandès, eduard, etc.} and the references
%% therein.
